### 2022-10-30 Group.Rmd
Add files via upload

---
title: "Group assignment"
author: "Alima Dzhanybaeva"
date: "2022-10-30"
output:
  pdf_document: default
  html_document: default
---
```{r include=FALSE}
library(tidyverse)
library(modelsummary)
library(knitr)
```
## 1.1 Overview of the original data.
### The original hotels-europe data includes information on price and features of hotels in 46 European cities and for 2017-2018. The data was downloaded from https://osf.io/yzntm/download.
### Table 1.1 shows the main variables, their description and type.
```{r include=FALSE}
variables <- c('hotel_id','accommodation_type', 'addresscountryname', 'weekend', 'holiday',
               'center1distance', 'starrating', 'guestreviewrating', 'price', 'price_night',
               'year', 'month')
info <- c('Hotel ID', 'Type of accomodation', 'Country', 'Flag, if day is a weekend',
          'Flag, if day is a public holiday', 'Distance from main city center',
          'Number of stars', 'User rating average', 'Price in EUR', 'Number of nights',
          'Year (YYYY)', 'Month (MM)')
type <- c('numeric', 'string', 'string', 'binary', 'binary', 'string',
          'numeric', 'string', 'numeric', 'string', 'numeric', 'numeric')
description <- data.frame(variables, info, type)
```
```{r echo=FALSE}
kable(description, caption = "Table 1.1 Description of the main variables in the original dataset")
```
## 1.2 Dataset for 7 Central European countries
### For our analysis we used 7 Central European countries: Czech Republic, Germany, Italy, Hungary, Austria, Poland, Slovakia.
```{r}
df <- read.csv('https://osf.io/yzntm/download')
df2 <- df %>% filter(addresscountryname %in% 
                       c('Czech Republic', 'Germany', 'Italy', 
                         'Hungary', 'Austria', 'Poland', 'Slovakia'))

```
### The folowing manipulations were carried out on the original data to change the existing variables and to add new ones:
* The type of the variables *center1distance* and *guestreviewrating* were changed from 'string' to 'numeric'
```{r include=FALSE}
# guestreviewrating separation
df2 <- separate(df2, guestreviewsrating, ' /', into =
                 c('actualrating', 'rate'))
df2 <- select(df2, -rate)
df2$actualrating <- as.numeric(df2$actualrating)

# Distance
df2 <- separate(df2, center1distance, ' ', into =
                  c('distance', 'miles'))
df2 <- select(df2, -miles)
df2$distance <- as.numeric(df2$distance)
```
* The original *accommodationtype* variable was tranformed into new *accomtype* factor variable.
```{r}
df2 <- separate(df2, accommodationtype, '@', into = 
                 c('word', 'acctype'))
df2 <- select(df2, -word)
df2 <- mutate(df2, acctype_f = factor(acctype))
```
* *trueprice* variable was generated by dividing the original *price* variable by *price_night*
```{r}
df2 <- separate(df2, price_night, ' ', into =
                     c('pr','word', 'nights', 'night'))
df2 <- select(df2, -pr)
df2 <- select(df2, -night)
df2 <- select(df2, -word)
df2$nights <- as.numeric(df2$nights)
df2$trueprice <- df2$price/df2$nights
```
* *season* variable was created based on the *month* variable
```{r}
df2 <- df2 %>%
  mutate(season = case_when(month == 12 | month == 1 |month == 2 ~ 'winter',
                            month == 3 | month == 4 |month == 5 ~ 'spring',
                            month == 6 | month == 7 |month == 8 ~ 'summer',
                            month == 9 | month == 10 |month == 11 ~ 'autumn'))
```
* With the help of the existing *starrating* variable new *class* variable was generated
```{r}
df2 <- df2 %>%
  mutate(class = case_when(starrating == 0.0 | starrating == 1.0 ~ 'tourist',
                           starrating == 1.5 | starrating == 2.0 ~ 'standard',
                           starrating == 2.5 | starrating == 3.0 ~ 'comfort',
                           starrating == 3.5 | starrating == 4.0 ~ 'first class',
                           starrating == 4.5 | starrating == 5.0 ~ 'luxury'))
```

## Summary of the transformed dataset
```{r}
datasummary(starrating + actualrating + trueprice ~ Mean + Min + Max + SD, data = df2)
```

### 2022-11-01 Draft.Rmd
Add files via upload

---
title: "DRAFT"
author: "Alima Dzhanybaeva"
date: "2022-10-31"
output:
  pdf_document:
         latex_engine: xelatex
  html_document: default
---
```{r include=FALSE}
library(tidyverse)
library(modelsummary)
library(dplyr)
library(knitr)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```
## 1.1 Overview of the original data.
### The original hotels-europe data includes information on price and features of hotels in 46 European cities and for 2017-2018. The data was downloaded from https://osf.io/yzntm/download.
### Table 1.1 shows the main variables, their description and type.
```{r include=FALSE}
variables <- c('hotel_id','accommodation_type', 'addresscountryname', 'weekend', 'holiday',
               'center1distance', 'starrating', 'guestreviewrating', 'price', 'price_night',
               'year', 'month')
info <- c('Hotel ID', 'Type of accomodation', 'Country', 'Flag, if day is a weekend',
          'Flag, if day is a public holiday', 'Distance from main city center',
          'Number of stars', 'User rating average', 'Price in EUR', 'Number of nights',
          'Year (YYYY)', 'Month (MM)')
type <- c('numeric', 'string', 'string', 'binary', 'binary', 'string',
          'numeric', 'string', 'numeric', 'string', 'numeric', 'numeric')
description <- data.frame(variables, info, type)
```
```{r}
kable(description, caption = "Table 1.1 Description of the main variables in the original dataset")
```
## 1.2 Dataset for 7 Central European countries
### For our analysis we used 7 Central European countries: Czech Republic, Germany, Italy, Hungary, Austria, Poland, Slovakia.
```{r}
df <- read.csv('https://osf.io/yzntm/download')
df2 <- df %>% filter(addresscountryname %in% 
                       c('Czech Republic', 'Germany', 'Italy', 
                         'Hungary', 'Austria', 'Poland', 'Slovakia'))

```
### The folowing manipulations were carried out on the original data to change the existing variables and to add new ones:
* The type of the variables *center1distance* and *guestreviewrating* were changed from 'string' to 'numeric'
```{r include=FALSE}
# guestreviewrating separation
df2 <- separate(df2, guestreviewsrating, ' /', into =
                 c('actualrating', 'rate'))
df2 <- select(df2, -rate)
df2$actualrating <- as.numeric(df2$actualrating)

# Distance
df2 <- separate(df2, center1distance, ' ', into =
                  c('distance', 'miles'))
df2 <- select(df2, -miles)
df2$distance <- as.numeric(df2$distance)
```
* The original *accommodationtype* variable was tranformed into new *accomtype* factor variable.
```{r}
df2 <- separate(df2, accommodationtype, '@', into = 
                 c('word', 'acctype'))
df2 <- select(df2, -word)
df2 <- mutate(df2, acctype_f = factor(acctype))
```
* *trueprice* variable was generated by dividing the original *price* variable by *price_night*
```{r}
df2 <- separate(df2, price_night, ' ', into =
                     c('pr','word', 'nights', 'night'))
df2 <- select(df2, -pr)
df2 <- select(df2, -night)
df2 <- select(df2, -word)
df2$nights <- as.numeric(df2$nights)
df2$trueprice <- df2$price/df2$nights
```
* *season* variable was created based on the *month* variable
```{r}
df2 <- df2 %>%
  mutate(season = case_when(month == 12 | month == 1 |month == 2 ~ 'winter',
                            month == 3 | month == 4 |month == 5 ~ 'spring',
                            month == 6 | month == 7 |month == 8 ~ 'summer',
                            month == 9 | month == 10 |month == 11 ~ 'autumn'))
```
* With the help of the existing *starrating* variable new *class* variable was generated
```{r}
df2 <- df2 %>%
  mutate(class = case_when(starrating == 0.0 | starrating == 1.0 ~ 'tourist',
                           starrating == 1.5 | starrating == 2.0 ~ 'standard',
                           starrating == 2.5 | starrating == 3.0 ~ 'comfort',
                           starrating == 3.5 | starrating == 4.0 ~ 'first class',
                           starrating == 4.5 | starrating == 5.0 ~ 'luxury'))
```
## Summary of the transformed dataset
```{r}
datasummary(distance + starrating + actualrating + trueprice ~ Mean + Min + Max + SD, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

### Histogram for distances
```{r}
ggplot(data=df2, aes(x=distance)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
  labs(x='Distance', y='Count')
```

### Histogram for starrating
```{r}
ggplot(data=df2, aes(x=starrating)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
  labs(x='Stars', y='Count')
```

### Histogram for guest ratings
```{r message=FALSE}
ggplot(data=df2, aes(x=actualrating)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Guest reviews', y='Count')
```

### Histogram for prices
```{r message=FALSE}
ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Price', y='Count') 
ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Price', y='Count') + xlim(0, 1200) 
```

### Accommodation type
```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n)))
```

### Country
```{r echo=FALSE}
kable(count(df2, addresscountryname) %>% arrange(desc(n)))
```

### Weekend and holiday
```{r echo=FALSE}
kable(count(df2, weekend))
```
```{r echo=FALSE}
kable(count(df2, holiday))
```
### Year and month
```{r echo=FALSE}
kable(count(df2, year))
```
```{r echo=FALSE}
kable(count(df2, month))
```
### Season and class
```{r echo=FALSE}
kable(count(df2, season) %>% arrange(desc(n)))
```
```{r echo=FALSE}
kable(count(df2, class))
```

## Findings
### Mean prices for countries
```{r}
datasummary(trueprice*addresscountryname ~ Mean + Max + Min, data=df2)
```

### Ratings for diff countries
```{r}
datasummary(actualrating*addresscountryname ~ Mean, data=df2)
```

### Plot for diff years diff countries
```{r}
df3 <- aggregate(trueprice ~ addresscountryname + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=addresscountryname)) + 
  geom_bar(stat='identity') + facet_wrap(~addresscountryname) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2)
```

### Mean prices for diff seasons
```{r}
datasummary(trueprice*season ~ Mean, data=df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

### Plot for classes
```{r message=FALSE}
datasummary(trueprice*class ~ Mean, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 
  geom_bar(stat = 'summary') + labs(x='Class', y='Price', fill = 'Class')
```

### 2022-11-01 Draft.Rmd
Update Draft.Rmd
#missing values - data quality overview

@@
 ```
+### Quality of the dataset - missing values overview
+
+```{r}
+df2 %>% 
+  skimr::skim_without_charts() 
+```
+
 ## 1.2 Dataset for 7 Central European countries

### 2022-11-01 Draft.Rmd
Update Draft.Rmd
non-zero values check

@@
 ```
-### Quality of the dataset - missing values overview
+### Quality of the dataset - missing values overview and frequency distribution of numeric values
 
@@
   skimr::skim_without_charts() 
+```
+
+### Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
+```{r}
+kable(funModeling::df_status(df))
 ```

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

--- 2022-11-01 Draft.Rmd
@@
 ### The original hotels-europe data includes information on price and features of hotels in 46 European cities and for 2017-2018. The data was downloaded from https://osf.io/yzntm/download.
-### Table 1.1 shows the main variables, their description and type.
+
 ```{r include=FALSE}
@@
 ```{r}
-kable(description, caption = "Table 1.1 Description of the main variables in the original dataset")
+kable(description, caption = "Description of the main variables in the original dataset")
 ```
+
+### • Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
+```{r include=FALSE}
+df <- read.csv('https://osf.io/yzntm/download')
+```
+```{r}
+kable(funModeling::df_status(df))
+```
+
 ## 1.2 Dataset for 7 Central European countries
-### For our analysis we used 7 Central European countries: Czech Republic, Germany, Italy, Hungary, Austria, Poland, Slovakia.
+### • For our analysis we used 7 Central European countries: Czech Republic, Germany, Italy, Hungary, Austria, Poland, Slovakia.
 ```{r}
-df <- read.csv('https://osf.io/yzntm/download')
 df2 <- df %>% filter(addresscountryname %in% 
@@
 ```
-### The folowing manipulations were carried out on the original data to change the existing variables and to add new ones:
+
+### • The folowing manipulations were carried out on the original data to change the existing variables and to add new ones:
 * The type of the variables *center1distance* and *guestreviewrating* were changed from 'string' to 'numeric'
@@
 ```
+
+### • Quality of the dataset - missing values overview and frequency distribution of numeric values
+
+```{r}
+df2 %>% 
+  skimr::skim_without_charts() 
+```
+
 ## Summary of the transformed dataset
@@
 
-### Histogram for distances
+### • Histogram for distances
 ```{r}
@@
 
-### Histogram for starrating
+### • Histogram for starrating
 ```{r}
@@
 
-### Histogram for guest ratings
+### • Histogram for guest ratings
 ```{r message=FALSE}
@@
 
-### Histogram for prices
+### • Histogram for prices
 ```{r message=FALSE}
@@
 
-### Accommodation type
+### • Accommodation type
 ```{r echo=FALSE}
@@
 
-### Country
+### • Country
 ```{r echo=FALSE}
@@
 
-### Weekend and holiday
+### • Weekend and holiday
 ```{r echo=FALSE}
@@
 ```
-### Year and month
+### • Year and month
 ```{r echo=FALSE}
@@
 ```
-### Season and class
+### • Season and class
 ```{r echo=FALSE}
@@
 ## Findings
-### Mean prices for countries
+### • Mean prices for countries
 ```{r}
@@
 
-### Ratings for diff countries
+### • Ratings for diff countries
 ```{r}
@@
 
-### Plot for diff years diff countries
+### • Plot for diff years diff countries
 ```{r}
@@
 
-### Mean prices for diff seasons
+### • Mean prices for diff seasons
 ```{r}
@@
 
-### Plot for classes
+### • Plot for classes
 ```{r message=FALSE}

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

@@
 ```
-```{r}
+```{r include=FALSE}
 kable(description, caption = "Description of the main variables in the original dataset")
@@
 ### • The folowing manipulations were carried out on the original data to change the existing variables and to add new ones:
-* The type of the variables *center1distance* and *guestreviewrating* were changed from 'string' to 'numeric'
+* The type of the variables *center1distance* and *guestreviewsrating* were changed from 'string' to 'numeric'. The new variable names are *distance* and *actualrating * respectively.
 ```{r include=FALSE}
@@
 df2 <- df2 %>%
-  mutate(class = case_when(starrating == 0.0 | starrating == 1.0 ~ 'tourist',
-                           starrating == 1.5 | starrating == 2.0 ~ 'standard',
-                           starrating == 2.5 | starrating == 3.0 ~ 'comfort',
-                           starrating == 3.5 | starrating == 4.0 ~ 'first class',
-                           starrating == 4.5 | starrating == 5.0 ~ 'luxury'))
+  mutate(class = case_when(starrating == 1.0 | starrating == 1.5 ~ 'tourist',
+                           starrating == 2.0 | starrating == 2.5 ~ 'standard',
+                           starrating == 3.0 | starrating == 3.5 ~ 'comfort',
+                           starrating == 4.0 | starrating == 4.5 ~ 'first class',
+                           starrating == 5.0 ~ 'luxury'))
 ```
@@
 
-## Summary of the transformed dataset
-```{r}
+## Summary for the main variables in the transformed dataset
+### __Numeric variables__
+```{r echo=FALSE}
 datasummary(distance + starrating + actualrating + trueprice ~ Mean + Min + Max + SD, data = df2) %>%
@@
 
-### • Histogram for distances
-```{r}
+* Distance
+75% of the hotels are located between 0 and 2.4 miles from the main city center. 
+The histogram below shows the distribution of the distances from the city center, the limit for x-axis was set at 25 miles.
+```{r echo=FALSE}
 ggplot(data=df2, aes(x=distance)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
@@
 
-### • Histogram for starrating
-```{r}
+* Starrating
+Most of hotels from the dataset have 3 and 4 stars.
+```{r echo=FALSE}
 ggplot(data=df2, aes(x=starrating)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
-  labs(x='Stars', y='Count')
+  labs(x='Stars', y='Count') + xlim(1,5)
 ```
 
-### • Histogram for guest ratings
-```{r message=FALSE}
+* Actualrating
+As we can see from the histogram below, 80% of the guest reviews are between 3.4 and 4.1.
+```{r echo=FASLE, message=FALSE}
 ggplot(data=df2, aes(x=actualrating)) + geom_histogram(fill='navyblue', color='white') + 
@@
 
-### • Histogram for prices
-```{r message=FALSE}
-ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
-  labs(x='Price', y='Count') 
+* Trueprice
+99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
+The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
+```{r echo=FALSE, message=FALSE}
 ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
@@
 ```
-
+* Year and month
+```{r echo=FALSE}
+kable(count(df2, year))
+```
+```{r echo=FALSE}
+kable(count(df2, month))
+```
 ### • Accommodation type
@@
 ```
-### • Year and month
-```{r echo=FALSE}
-kable(count(df2, year))
-```
-```{r echo=FALSE}
-kable(count(df2, month))
-```
+
 ### • Season and class

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

@@
 
-## Summary for the main variables in the transformed dataset
-### __Numeric variables__
+## • Summary for the main variables in the transformed dataset
+## __Numeric variables__
 ```{r echo=FALSE}
@@
 
-* Distance
+### • Distance
 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
@@
 
-* Starrating
+### • Starrating
 Most of hotels from the dataset have 3 and 4 stars.
@@
 
-* Actualrating
+### • Actualrating
 As we can see from the histogram below, 80% of the guest reviews are between 3.4 and 4.1.
-```{r echo=FASLE, message=FALSE}
+```{r echo=FALSE, message=FALSE}
 ggplot(data=df2, aes(x=actualrating)) + geom_histogram(fill='navyblue', color='white') + 
@@
 
-* Trueprice
+### • Trueprice
 99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
@@
 ```
-* Year and month
+### • Year and month
 ```{r echo=FALSE}

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

@@
 ```
-```{r include=FALSE}
+```{r echo=FALSE}
 kable(description, caption = "Description of the main variables in the original dataset")
@@
 ### • Distance
-75% of the hotels are located between 0 and 2.4 miles from the main city center. 
+### 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
 The histogram below shows the distribution of the distances from the city center, the limit for x-axis was set at 25 miles.
@@
 ### • Starrating
-Most of hotels from the dataset have 3 and 4 stars.
+### Most of hotels from the dataset have 3 and 4 stars.
 ```{r echo=FALSE}
@@
 ### • Actualrating
-As we can see from the histogram below, 80% of the guest reviews are between 3.4 and 4.1.
+### As we can see from the histogram below, 80% of the guest reviews are between 3.4 and 4.1.
 ```{r echo=FALSE, message=FALSE}
@@
 ### • Trueprice
-99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
-The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
+### 99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
+### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
 ```{r echo=FALSE, message=FALSE}

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

@@
 ### 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
-The histogram below shows the distribution of the distances from the city center, the limit for x-axis was set at 25 miles.
+### The histogram below shows the distribution of the distances from the city center, the limit for x-axis was set at 25 miles.
 ```{r echo=FALSE}
@@
 ```
+
 ### • Year and month
@@
 
-## Findings
+## 1.3 Findings
 ### • Mean prices for countries
-```{r}
-datasummary(trueprice*addresscountryname ~ Mean + Max + Min, data=df2)
-```
-
-### • Ratings for diff countries
-```{r}
-datasummary(actualrating*addresscountryname ~ Mean, data=df2)
+```{r echo=FALSE}
+datasummary(trueprice*addresscountryname ~ Mean + Max + Min, data=df2) %>%
+   kableExtra::kable_styling(latex_options = "hold_position")
 ```

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

@@
 ## • Summary for the main variables in the transformed dataset
-## __Numeric variables__
+## *Numeric variables*
 ```{r echo=FALSE}
@@
 ```
+
+### *Factor variables*
+
 ### • Accommodation type
@@
 
+### • Season and class
+```{r echo=FALSE}
+kable(count(df2, season) %>% arrange(desc(n)))
+```
+```{r echo=FALSE}
+kable(count(df2, class))
+```
+
+### *Binary variables*
+
 ### • Weekend and holiday
@@
 kable(count(df2, holiday))
-```
-
-### • Season and class
-```{r echo=FALSE}
-kable(count(df2, season) %>% arrange(desc(n)))
-```
-```{r echo=FALSE}
-kable(count(df2, class))
 ```
@@
 ### • Mean prices for diff seasons
-```{r}
+```{r echo=FALSE}
 datasummary(trueprice*season ~ Mean, data=df2) %>%
@@
 ### • Plot for classes
-```{r message=FALSE}
+```{r echo=FALSE, message=FALSE}
 datasummary(trueprice*class ~ Mean, data = df2) %>%
    kableExtra::kable_styling(latex_options = "hold_position")
+```
+```{r echo=FALSE}
 ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

@@
 df2$distance <- as.numeric(df2$distance)
+
+df2$country <- as.factor(df2$addresscountryname)
+df2 <- select(df2, -addresscountryname)
 ```
-* The original *accommodationtype* variable was tranformed into new *accomtype* factor variable.
+* The original *accommodationtype* variable was tranformed into new *acctype_f* factor variable.
 ```{r}
@@
                             month == 9 | month == 10 |month == 11 ~ 'autumn'))
+df2$season <- as.factor(df2$season)
 ```
@@
                            starrating == 5.0 ~ 'luxury'))
+df2$class <- as.factor(df2$class)
 ```
@@
 
-### *Factor variables*
+## *Factor variables*
 
@@
 ```{r echo=FALSE}
-kable(count(df2, addresscountryname) %>% arrange(desc(n)))
+kable(count(df2, country) %>% arrange(desc(n)))
 ```
@@
 
-### *Binary variables*
+## *Binary variables*
 
@@
 ```{r echo=FALSE}
-datasummary(trueprice*addresscountryname ~ Mean + Max + Min, data=df2) %>%
+datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
    kableExtra::kable_styling(latex_options = "hold_position")
@@
 ```{r}
-df3 <- aggregate(trueprice ~ addresscountryname + year, 
+df3 <- aggregate(trueprice ~ country + year, 
                  data=df2, 
@@
                  })
-ggplot(data = df3, aes(x=year, y=trueprice, fill=addresscountryname)) + 
-  geom_bar(stat='identity') + facet_wrap(~addresscountryname) +
+ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
+  geom_bar(stat='identity') + facet_wrap(~country) +
   geom_text(aes(label = round(trueprice)), vjust = -0.2)

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

@@
 ### • Year and month
+### 22636 records from the dataset are for the year 2017 and 32311 - for 2018.
 ```{r echo=FALSE}
-kable(count(df2, year))
+kable(count(df2, year)) %>%
+  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
 ```
+
+### Winter and spring are fully presented in the dataset, whereas there are no records for July, August, September, and October.
 ```{r echo=FALSE}
-kable(count(df2, month))
+kable(count(df2, month)) %>%
+  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
 ```
@@
 ### • Accommodation type
+### There are 16 unique accommodation types in the dataset. The most numerous types are "Hotel",  "Apartment", "Guest House",  and "Bed and Breakfast". Together they make up 93% of all records.
 ```{r echo=FALSE}
-kable(count(df2,acctype_f) %>% arrange(desc(n)))
+kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
+  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
 ```
@@
 ### • Country
+### The countries with the most records are Italy and Germany. Together they make up 66% of all records.
 ```{r echo=FALSE}
-kable(count(df2, country) %>% arrange(desc(n)))
+kable(count(df2, country) %>% arrange(desc(n))) %>%
+  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
 ```
@@
 ### • Season and class
+### As we observed earlier, the dataset did not include two months for summer and two months for autumn, consequently, spring and winter have the most observations.
 ```{r echo=FALSE}
-kable(count(df2, season) %>% arrange(desc(n)))
+kable(count(df2, season) %>% arrange(desc(n))) %>%
+  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
+```
+
+### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars.There are also 15889 missing values.
+They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense.
+Therefore, these observations were omitted.
+```{r echo=FALSE}
+kable(count(df2, class)) %>%
+  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
 ```
 ```{r echo=FALSE}
-kable(count(df2, class))
+data <- data.frame(
+  class=c('comfort', 'first class', 'luxury', 'standard', 'tourist'),
+  value=c(17695, 14154, 2307, 4025, 877)
+)
+data <- data %>% 
+  arrange(desc(class)) %>%
+  mutate(prop = value / sum(data$value) *100) %>%
+  mutate(ypos = cumsum(prop)- 0.5*prop )
+
+ggplot(data, aes(x="", y=prop, fill=class)) +
+  geom_bar(stat="identity", width=1, color="white") +
+  coord_polar("y", start=0) +
+  theme_void() + 
+  geom_text(aes(y = ypos, label = round(prop, 1)), color = "white", size=5) +
+  scale_fill_brewer(palette="Set1") + labs(fill="Class")
 ```
@@
 ```{r echo=FALSE}
-kable(count(df2, weekend))
+kable(count(df2, weekend)) %>%
+  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
 ```
 ```{r echo=FALSE}
-kable(count(df2, holiday))
+kable(count(df2, holiday)) %>%
+  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
 ```

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

@@
 ### The countries with the most records are Italy and Germany. Together they make up 66% of all records.
-```{r echo=FALSE}
+```{r}
 kable(count(df2, country) %>% arrange(desc(n))) %>%
@@
 ```
+
 ```{r echo=FALSE}
@@
 ### • Mean prices for countries
+
 ```{r echo=FALSE}
-datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
+datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%
   kableExtra::kable_styling(latex_options = "hold_position")

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

@@
 ### • Weekend and holiday
+### 36193 records were made on weekends (66%),  and 18754 - on weekdays (34%)
+
 ```{r echo=FALSE}
@@
 ```
+
+### Only 21% (11728) of all observations were made on holidays.
+
 ```{r echo=FALSE}
@@
 
-## 1.3 Findings
+## 1.3 Findings. 
+### For this project, we wanted to find the best deal among different types of accommodation in Central European countries. 
+### Consequently, we formulated the question: 
+* *How does the average price change for different values of explanatory variables?*
+
 ### • Mean prices for countries
 
-```{r echo=FALSE}
+```{r}
 datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

@@
   geom_bar(stat='identity') + facet_wrap(~country) +
-  geom_text(aes(label = round(trueprice)), vjust = -0.2)
+  geom_text(aes(label = round(trueprice)), vjust = -0.2) +
+  scale_x_discrete() + ylim(0, 195) + 
+  labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
 ```
@@
 ```
-```{r echo=FALSE}
+```{r echo=FALSE, message=FALSE}
 ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 
-  geom_bar(stat = 'summary') + labs(x='Class', y='Price', fill = 'Class')
+  geom_bar(stat = 'summary') + labs(x='Class', y='Price for 1 night (in EUR)', fill = 'Class')
 ```

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

@@
 ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
-  labs(x='Price', y='Count') + xlim(0, 1200) 
+  labs(x='Price fpr one night (in EUR)', y='Count') + xlim(0, 600) 
 ```
@@
 ### Winter and spring are fully presented in the dataset, whereas there are no records for July, August, September, and October.
+
 ```{r echo=FALSE}
@@
 ### • Plot for classes
-```{r echo=FALSE, message=FALSE}
+```{r echo=FALSE}
 datasummary(trueprice*class ~ Mean, data = df2) %>%

### 2022-11-05 Draft.Rmd
Update Draft.Rmd
libraries

@@
 library(knitr)
+library(htmlTable)
+library(reshape)
+library(funModeling)
 ```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

--- 2022-11-03 Draft.Rmd
@@
 library(knitr)
+library(htmlTable)
 ```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 
-### • Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
 ```{r include=FALSE}
@@
 ```
-```{r}
-kable(funModeling::df_status(df))
-```
-
 ## 1.2 Dataset for 7 Central European countries
@@
   skimr::skim_without_charts() 
+```
+
+### • Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
+```{r}
+kable(funModeling::df_status(df))
 ```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 
-### • Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
-```{r}
-kable(funModeling::df_status(df))
+### • Some value are not blank but include zeros and inf. The next table checks these entries as well as unique values.
+```{r echo=FALSE, include=FALSE}
+zeros<-funModeling::df_status(df2)
+```
+
+```{r echo=FALSE, include=TRUE}
+kable(zeros)
 ```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 
+### There are prominent outliers for *distance* and *true price* variables, therefore, the dataset was transformed, setting the maximum values at the 99% percentile (35 miles and 600 EUR respectively).
+
+```{r echo=FALSE}
+df2 <- df2 %>% filter(distance < 35) %>% filter(trueprice < 600)
+datasummary(distance + trueprice ~ mean + Min + Max + SD, data = df2) %>%
+   kableExtra::kable_styling(latex_options = "hold_position")
+```
+
 ### • Distance
 ### 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
-### The histogram below shows the distribution of the distances from the city center, the limit for x-axis was set at 25 miles.
+### The histogram below shows the distribution of the distances from the city center.
+
 ```{r echo=FALSE}
 ggplot(data=df2, aes(x=distance)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
-  labs(x='Distance', y='Count')
+  labs(x='Distance from the city center (in miles)', y='Count')
 ```
@@
 ### • Trueprice
-### 99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
 ### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
+
 ```{r echo=FALSE, message=FALSE}
 ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
-  labs(x='Price fpr one night (in EUR)', y='Count') + xlim(0, 600) 
+  labs(x='Price for one night (in EUR)', y='Count') + xlim(0, 600) 
 ```
@@
 ### There are 16 unique accommodation types in the dataset. The most numerous types are "Hotel",  "Apartment", "Guest House",  and "Bed and Breakfast". Together they make up 93% of all records.
+
 ```{r echo=FALSE}
@@
 
-### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars.There are also 15889 missing values.
+### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars.
+There are also 15889 missing values.
 They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense.
@@
 ### • Weekend and holiday
-### 36193 records were made on weekends (66%),  and 18754 - on weekdays (34%)
+### 35362 records were made on weekends (66%),  and 18478 - on weekdays (34%)
 
@@
 
-### Only 21% (11728) of all observations were made on holidays.
+### Only 21% (11546) of all observations were made on holidays.
 
@@
 ### For this project, we wanted to find the best deal among different types of accommodation in Central European countries. 
-### Consequently, we formulated the question: 
-* *How does the average price change for different values of explanatory variables?*
+### Consequently, we formulated the following question: 
+* *How does the average price for accommodation change for different values of the following variables: year, country, distance, season, class?*
 
-### • Mean prices for countries
-
-```{r}
-datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%
-  kableExtra::kable_styling(latex_options = "hold_position")
-```
-
-### • Plot for diff years diff countries
+### • How the price for accommodation changed for 7 Central European countries in 2018 in comparison with 2017.
 ```{r}
@@
   labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
+```
+
+### As we can see from the graph, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
+### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.
+
+### • Mean prices for countries
+
+```{r}
+datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+### • Mean price/ distance
+
+```{r echo=FALSE, message=FALSE}
+ggplot(df2, aes(x = distance, y = trueprice))+
+  stat_summary_bin(fun = 'mean', bins = 80, 
+                   geom = 'point', color = 'red',
+                   size = 2) + 
+  labs(x='Distance from the city center', y='Price for one night(in EUR)')
+```
+
+```{r echo=FALSE, message=FALSE}
+ggplot(df2, aes(x = distance, y = trueprice))+
+  stat_summary_bin(fun = 'mean', bins = 50, 
+                   geom = 'point', color = 'red',
+                   size = 2) + 
+  labs(x='Distance from the city center', y='Price for one night(in EUR)') +
+  xlim(0,25)
 ```
@@
 ```
+
+### Weekend
+```{r}
+ggplot(data=df2, aes(x=weekend, y=trueprice, group=weekend))+
+  geom_violin(trim=FALSE, fill='#A4A4A4', color="darkred")+
+  geom_boxplot(width=0.1) + theme_minimal() + 
+  labs(x="Weekend", y="Price for one night (in EUR)")
+```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 ---
-title: "DRAFT"
-author: "Alima Dzhanybaeva"
-date: "2022-10-31"
+title: "Group assignment"
+author: "Alima Dzhanybaeva, Jana Hochel, Tasnim Murad"
+date: "2022-05-11"
 output:
@@
 ### • The folowing manipulations were carried out on the original data to change the existing variables and to add new ones:
-* The type of the variables *center1distance* and *guestreviewsrating* were changed from 'string' to 'numeric'. The new variable names are *distance* and *actualrating * respectively.
+* The type of the variables *center1distance* and *guestreviewsrating* were changed from 'string' to 'numeric', and from 'string' to 'factor' for *addresscountryname*.
+The new variable names are *distance*, *actualrating * and *country* respectively.
 ```{r include=FALSE}
@@
 ```
-* The original *accommodationtype* variable was tranformed into new *acctype_f* factor variable.
+* The original *accommodationtype* variable was transformed into new *acctype_f* factor variable.
 ```{r}
@@
 
-## 1.3 Findings. 
+## 1.3 Analysis 
 ### For this project, we wanted to find the best deal among different types of accommodation in Central European countries. 
 ### Consequently, we formulated the following question: 
-* *How does the average price for accommodation change for different values of the following variables: year, country, distance, season, class?*
+* *How does the average price for accommodation change for different values of the following variables: year, country, distance, season, class, weekend?*
 
-### • How the price for accommodation changed for 7 Central European countries in 2018 in comparison with 2017.
+## *Findings*
+
+### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
+### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.
 ```{r}
@@
 
-### As we can see from the graph, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
-### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.
-
-### • Mean prices for countries
+### • The lowest price is 12 EUR per night (Czech Republic),  whereas the lowest average cost is 86 EUR (Poland). On average, Austrian accommodation is the most expensive with a mean price of 158 EUR.
 
@@
 
-### • Mean price/ distance
+### • The eminent negative relationship between price and distance from the city center can be tracked only until 7.5 miles.
+After that point, the dependence of the accommodation cost on the *distance* variable becomes vaguer, as the points are much more dispersed and do not follow a specific pattern.
+Therefore, we can conclude that on average, the cheapest accommodation is 7.5 miles far from the city center.
 
@@
 
-### • Mean prices for diff seasons
+### • The prices for accommodation in the chosen 7 Central European countries are on average the lowest during autumn and are highest during spring.
+The difference between the lowest and the highest value is 35 euros.
+
 ```{r echo=FALSE}
@@
 
-### • Plot for classes
+### • As expected, the cheapest class is "tourist" (1 and 1.5 stars) with a mean price of 88 euros.
+However, the average cost for "standard" (2 and 2.5 stars) falls not that far apart from the best deal with the difference of only 5 euros.
+Conversely, the "luxury"  (5 stars) class is on average 140 euros more expensive than  "first class" (4 and 4.5 stars).
+### Consequently, the difference between mean prices becomes bigger with the number of stars.
+
 ```{r echo=FALSE}
@@
 
-### Weekend
-```{r}
+### • The average price for accommodation is 16 euros higher during weekends.
+Moreover, as we can see from the graph below: (1) the boxplot for weekends is comparatively taller than the one for weekdays, indicating that prices are more dispersed during the end of the week; (2) the upper quartile for weekends is farther from the median than for weekdays, meaning that the 75% percentile is higher.
+
+```{r echo=FALSE}
+df2 <- df2 %>%
+  mutate(weekend = case_when(weekend == 1 ~'weekend',
+                            weekend == 0 ~ 'weekday'))
+datasummary(trueprice*weekend ~ Mean, data = df2) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+```{r echo=FALSE}
 ggplot(data=df2, aes(x=weekend, y=trueprice, group=weekend))+
@@
 ```
+
+## *Summary*
+### For the chosen 7 Central European countries (with the maximum value for the *distance* variable set to 35 miles and to 600 euros for *trueprice* variable)  following conclusions on the best deal accross different accommodation types were made:
+* Compared to other countries, the average prices in Slovakia do not tend to drastically jump.
+* On average, the cheapest deals can be found in Poland.
+* The optimal distance from the city center is 7,5 miles.
+* Autumn is the best season for finding advantageous offers.
+* "Tourist" is the class with the lowest prices, however, "standard" is not much more expensive.
+* Accommodation on weekdays is not only cheaper, but the prices are also not as dispersed as on weekends.

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 ### • Year and month
-### 22636 records from the dataset are for the year 2017 and 32311 - for 2018.
+### 22270 records from the dataset are for the year 2017 and 31570 - for 2018.
 ```{r echo=FALSE}
@@
 kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
-  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```
@@
 ### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.
-```{r}
+
+```{r echo=FALSE}
 df3 <- aggregate(trueprice ~ country + year, 
@@
                    size = 2) + 
-  labs(x='Distance from the city center', y='Price for one night(in EUR)')
-```
-
-```{r echo=FALSE, message=FALSE}
-ggplot(df2, aes(x = distance, y = trueprice))+
-  stat_summary_bin(fun = 'mean', bins = 50, 
-                   geom = 'point', color = 'red',
-                   size = 2) + 
-  labs(x='Distance from the city center', y='Price for one night(in EUR)') +
-  xlim(0,25)
+  labs(x='Distance from the city center (in miles)', y='Price for one night (in EUR)') +
+  scale_x_continuous(limits = c(0, 35),
+                     breaks=seq(from=0, to=35, by=2.5))
 ```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
-  kableExtra::kable_styling(latex_options = "hold_position")
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
 ### The countries with the most records are Italy and Germany. Together they make up 66% of all records.
-```{r}
+```{r echo=FALSE}
 kable(count(df2, country) %>% arrange(desc(n))) %>%
-  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
 kable(count(df2, season) %>% arrange(desc(n))) %>%
-  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
 kable(count(df2, class)) %>%
-  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
 
-## *Findings*
+## *Findings:*
 
@@
 
-```{r}
-datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%
-  kableExtra::kable_styling(latex_options = "hold_position")
+```{r echo=FALSE}
+datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
 datasummary(trueprice*season ~ Mean, data=df2) %>%
-   kableExtra::kable_styling(latex_options = "hold_position")
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 ```
+### Plotting frequency of observations
 
+```{r}
+funModeling::plot_num(df2)
+```
 ### There are prominent outliers for *distance* and *true price* variables, therefore, the dataset was transformed, setting the maximum values at the 99% percentile (35 miles and 600 EUR respectively).
@@
 ### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars.
-There are also 15889 missing values.
+There are also 15720 missing values.
 They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense.

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

--- 2022-11-05 Draft.Rmd
@@
 ```
+\newpage
+
+### Frequency plot of observations
+
+```{r}
+funModeling::plot_num(df2)
+```
 
@@
 ```
-
 ### There are prominent outliers for *distance* and *true price* variables, therefore, the dataset was transformed, setting the maximum values at the 99% percentile (35 miles and 600 EUR respectively).

### 2022-11-05 draft_Tasnim.R
Add files via upload

@@ -1,0 +1,234 @@
+##title: "Finding the best deal among Central European hotels"
+##Take necessary packages in library
+library(tidyverse)
+library(modelsummary)
+library(dplyr)
+library(knitr)
+library(ggthemes)
+
+##clean the environment
+rm(list=ls())
+
+##Import data online
+df <- read.csv('https://osf.io/yzntm/download')
+
+glimpse(df)
+
+###Questions###
+#1. Clean the data and give a short overview
+#2. Summarize the main variables and plot their graphs
+#3. Find the correlation between price and distance
+#4. Find the correlation between guest reviewing report with distance and price
+#5. Test whether there is no statistical significant difference in the price of hotels between year 2017 and 2018
+#6. There is no statistical significant difference in the price of hotels between summer and winter season
+#7. Test whether there is any statistical significant difference in the review report of on the basis of starrating
+.
+
+###1. Clean the data and give a short overview
+
+## Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
+
+kable(funModeling::df_status(df))
+
+##The folowing manipulations were carried out on the original data to change the existing variables and to add new ones:
+#The type of the variables *center1distance* and *guestreviewsrating* were changed from 'string' to 'numeric'. The new variable names are *distance* *distance2* and *actualrating * respectively.
+
+# guestreviewrating separation
+
+df <- separate(df, guestreviewsrating, ' /', into =
+                 c('actualrating', 'rate'))
+df <- select(df, -rate)
+df$actualrating <- as.numeric(df$actualrating)
+
+
+# Distance from city center 1
+df <- separate(df, center1distance, ' ', into =
+                 c('distance', 'miles')) 
+df <- select(df, -miles)
+df$distance <- as.numeric(df$distance)
+
+
+# Distance from city center 2
+df <- separate(df, center2distance, ' ', into =
+                 c('distance2', 'miles')) 
+df <- select(df, -miles)
+df$distance2 <- as.numeric(df$distance2)
+
+# country as factor variable
+df$country <- as.factor(df$addresscountryname)
+df <- select(df, -addresscountryname)
+
[…]

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 
+### Correlation - what we can expect we opting for higher price?
+#### We may see that higher price is linked to proximity to the city center, higher rating, and more reviews.
+```{r echo=FALSE}
+# subset
+df3<-df2[c("price","trueprice","actualrating","rating_reviewcount","distance")]
+correlationt<-funModeling::correlation_table(data=df3, target="price") 
+```
+```{r echo=FALSE}
+kable(correlationt)
+```
+
 ### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

--- 2022-11-05 Draft.Rmd
@@
 
+### Correlation - what we can expect we opting for higher price?
+```{r echo=FALSE}
+# subset
+df3<-df2[c("price","trueprice","actualrating","rating_reviewcount","distance")]
+correlationt<-funModeling::correlation_table(data=df3, target="price") 
+```
+```{r echo=FALSE}
+kable(correlationt)
+```
+#### We may see that higher price is linked to proximity to the city center, higher rating, and more reviews.
+
 ### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

--- 2022-11-05 Draft.Rmd
@@
 
+### Correlation - what we can expect we opting for higher price?
+```{r echo=FALSE}
+# subset
+df3<-df2[c("trueprice","actualrating","rating_reviewcount","distance")]
+correlationt<-funModeling::correlation_table(data=df3, target="trueprice") 
+```
+```{r echo=FALSE}
+kable(correlationt)
+```
+#### We may see that higher price is linked to proximity to the city center, higher rating, and more reviews.
+
 ### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 ```
+###2. There is no statistically significant difference in the price of hotels between summer and winter season
+```{r echo=FALSE}
+t.test(df2$trueprice [df2$season=="winter"],df2$trueprice [df2$season=="summer"], mu=0, alt='two.sided', conf=0.95, paired=F)
+#Null Hypothesis is rejected
+
+```
 
@@
 
+## Time
 ### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
@@
 
+## Hypothesis testing for Time
+
+###1. Is there any statistical significant difference in the hotel price per night between year 2017 and 2018
+```{r echo=FALSE}
+t.test(df2$trueprice [df2$year=="2017"],df2$trueprice [df2$year=="2018"], mu=0, alt='two.sided', conf=0.95, paired=F)
+#(welsch1)
+#Null Hypothesis is rejected though the t-statistic is insignificant 
+```
+
+## Country
+
 ### • The lowest price is 12 EUR per night (Czech Republic),  whereas the lowest average cost is 86 EUR (Poland). On average, Austrian accommodation is the most expensive with a mean price of 158 EUR.
@@
 ```
+
+## Distance
 
@@
                      breaks=seq(from=0, to=35, by=2.5))
+```
+
+###1. Find the correlation between truelprice and distance 
+```{r echo=FALSE}
+corr_table1 <- df2 %>% 
+  select(country, trueprice, distance) %>% 
+  group_by(country) %>% 
+  summarise(correlation = cor(trueprice,distance))
+```
+
+```{r echo=FALSE}
+kable(corr_table1)
+```
+# Graph to show the correlation pattern by each country:
+```{r echo=FALSE}
+ggplot(corr_table1, aes(x = correlation ,
+                       y = fct_reorder(country, correlation))) +
+  geom_point(color = 'red', size = 2)+
+  labs(y='Countries',x='Correlation')
+```
+
+#### As we may see, staying in the center is less valued in Austria and Slovakia.
+
+###2. Find the correlation between guest reviewing report with distance and price
+```{r echo=FALSE}
+corr_table2 <- cor(df2[, c('trueprice','actualrating','distance')])
+```
+```{r echo=FALSE}
+kable(corr_table2)
 ```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

--- 2022-11-05 Draft.Rmd
@@
 ```
-
-### • Quality of the dataset - missing values overview and frequency distribution of numeric values
+\newpage
+## 1.2  Quality of the dataset
+### • Missing values overview and frequency distribution of numeric values
 
@@
 
-### Frequency plot of observations
-
-```{r}
-funModeling::plot_num(df2)
-```
-
+## 1.3 Descriptive statistics
 ## • Summary for the main variables in the transformed dataset
@@
 ```
+### Frequency plot of observations
 
-### • Distance
+```{r}
+funModeling::plot_num(df2)
+```
+
+### 1.3.1 Distance
 ### 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
@@
 
-### • Starrating
+### 1.3.2 Starrating
 ### Most of hotels from the dataset have 3 and 4 stars.
@@
 
-### • Actualrating
+### 1.3.3 Actualrating
 ### As we can see from the histogram below, 80% of the guest reviews are between 3.4 and 4.1.
@@
 
-### • Trueprice
+### 1.3.4 Trueprice
 ### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
@@
 
-### • Year and month
+### 1.3.5 Year and month
 ### 22270 records from the dataset are for the year 2017 and 31570 - for 2018.
@@
 ```
-
 ### Winter and spring are fully presented in the dataset, whereas there are no records for July, August, September, and October.
@@
 ```
-
 ## *Factor variables*
 
-### • Accommodation type
+### 1.3.6 Accommodation type
 ### There are 16 unique accommodation types in the dataset. The most numerous types are "Hotel",  "Apartment", "Guest House",  and "Bed and Breakfast". Together they make up 93% of all records.
@@
 
-### • Country
+### 1.3.7 Country
 ### The countries with the most records are Italy and Germany. Together they make up 66% of all records.
@@
 
-### • Season and class
+### 1.3.8 Season and class
 ### As we observed earlier, the dataset did not include two months for summer and two months for autumn, consequently, spring and winter have the most observations.
@@
 
-### • Weekend and holiday
+### 1.3.9 Weekend and holiday
 ### 35362 records were made on weekends (66%),  and 18478 - on weekdays (34%)
@@
   kableExtra::kable_styling(position = "center", latex_options = "hold_position")
-```
-
-## 1.3 Analysis 
-### For this project, we wanted to find the best deal among different types of accommodation in Central European countries. 
-### Consequently, we formulated the following question: 
-* *How does the average price for accommodation change for different values of the following variables: year, country, distance, season, class, weekend?*
-
-## *Findings:*
-
-### Correlation - what we can expect we opting for higher price?
-```{r echo=FALSE}
-# subset
-df3<-df2[c("trueprice","actualrating","rating_reviewcount","distance")]
-correlationt<-funModeling::correlation_table(data=df3, target="trueprice") 
-```
-```{r echo=FALSE}
-kable(correlationt)
-```
-#### We may see that higher price is linked to proximity to the city center, higher rating, and more reviews.
-
-### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
-### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.
-
-```{r echo=FALSE}
-df3 <- aggregate(trueprice ~ country + year, 
-                 data=df2, 
-                 function(x) { 
-                   c(mean_price = mean(x)) 
-                 })
-ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
-  geom_bar(stat='identity') + facet_wrap(~country) +
-  geom_text(aes(label = round(trueprice)), vjust = -0.2) +
-  scale_x_discrete() + ylim(0, 195) + 
-  labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
-```
-
-### • The lowest price is 12 EUR per night (Czech Republic),  whereas the lowest average cost is 86 EUR (Poland). On average, Austrian accommodation is the most expensive with a mean price of 158 EUR.
-
-```{r echo=FALSE}
-datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-### • The eminent negative relationship between price and distance from the city center can be tracked only until 7.5 miles.
-After that point, the dependence of the accommodation cost on the *distance* variable becomes vaguer, as the points are much more dispersed and do not follow a specific pattern.
-Therefore, we can conclude that on average, the cheapest accommodation is 7.5 miles far from the city center.
-
-```{r echo=FALSE, message=FALSE}
-ggplot(df2, aes(x = distance, y = trueprice))+
-  stat_summary_bin(fun = 'mean', bins = 80, 
-                   geom = 'point', color = 'red',
-                   size = 2) + 
-  labs(x='Distance from the city center (in miles)', y='Price for one night (in EUR)') +
-  scale_x_continuous(limits = c(0, 35),
-                     breaks=seq(from=0, to=35, by=2.5))
 ```
@@
 
+## 1.4 Analysis 
+### For this project, we wanted to find the best deal among different types of accommodation in Central European countries. 
+### Consequently, we formulated the following question: 
+* *How does the average price for accommodation change for different values of the following variables: year, country, distance, season, class, weekend?*
+
+## *Findings:*
+
+### Correlation - what we can expect we opting for higher price?
+```{r echo=FALSE}
+# subset
+df3<-df2[c("trueprice","actualrating","rating_reviewcount","distance")]
+correlationt<-funModeling::correlation_table(data=df3, target="trueprice") 
+```
+```{r echo=FALSE}
+kable(correlationt)
+```
+#### We may see that higher price is linked to proximity to the city center, higher rating, and more reviews.
+
+## 1.4.1 Time
+### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
+### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.
+
+```{r echo=FALSE}
+df3 <- aggregate(trueprice ~ country + year, 
+                 data=df2, 
+                 function(x) { 
+                   c(mean_price = mean(x)) 
+                 })
+ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
+  geom_bar(stat='identity') + facet_wrap(~country) +
+  geom_text(aes(label = round(trueprice)), vjust = -0.2) +
+  scale_x_discrete() + ylim(0, 195) + 
+  labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
+```
+
+## 1.4.2 Country
+
+### • The lowest price is 12 EUR per night (Czech Republic),  whereas the lowest average cost is 86 EUR (Poland). On average, Austrian accommodation is the most expensive with a mean price of 158 EUR.
+
+```{r echo=FALSE}
+datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+# Graph to show the correlation pattern by each country:
+```{r echo=FALSE}
+ggplot(corr_table1, aes(x = correlation ,
+                       y = fct_reorder(country, correlation))) +
+  geom_point(color = 'red', size = 2)+
+  labs(y='Countries',x='Correlation')
+```
+
+## 1.4.3 Distance
+
+### • The eminent negative relationship between price and distance from the city center can be tracked only until 7.5 miles.
+After that point, the dependence of the accommodation cost on the *distance* variable becomes vaguer, as the points are much more dispersed and do not follow a specific pattern.
+Therefore, we can conclude that on average, the cheapest accommodation is 7.5 miles far from the city center.
+
+```{r echo=FALSE, message=FALSE}
+ggplot(df2, aes(x = distance, y = trueprice))+
+  stat_summary_bin(fun = 'mean', bins = 80, 
+                   geom = 'point', color = 'red',
+                   size = 2) + 
+  labs(x='Distance from the city center (in miles)', y='Price for one night (in EUR)') +
+  scale_x_continuous(limits = c(0, 35),
+                     breaks=seq(from=0, to=35, by=2.5))
+```
+
+### The correlation between truelprice and distance 
+```{r echo=FALSE}
+corr_table1 <- df2 %>% 
+  select(country, trueprice, distance) %>% 
+  group_by(country) %>% 
+  summarise(correlation = cor(trueprice,distance))
+```
+
+```{r echo=FALSE}
+kable(corr_table1)
+```
+
+#### As we may see, staying in the center is less valued in Austria and Slovakia.
+
+### The correlation between guest reviewing report with distance and price
+```{r echo=FALSE}
+corr_table2 <- cor(df2[, c('trueprice','actualrating','distance')])
+```
+```{r echo=FALSE}
+kable(corr_table2)
+```
+
+## 1.5 Hypothesis testing
+
+### 1.5.1 Is there any statistical significant difference in the hotel price per night between year 2017 and 2018
+```{r echo=FALSE}
+t.test(df2$trueprice [df2$year=="2017"],df2$trueprice [df2$year=="2018"], mu=0, alt='two.sided', conf=0.95, paired=F)
+#(welsch1)
+#Null Hypothesis is rejected though the t-statistic is insignificant 
+```
+### 1.5.2 There is no statistically significant difference in the price of hotels between summer and winter season
+```{r echo=FALSE}
+t.test(df2$trueprice [df2$season=="winter"],df2$trueprice [df2$season=="summer"], mu=0, alt='two.sided', conf=0.95, paired=F)
+#Null Hypothesis is rejected
+
+```
+
 ## *Summary*

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 ## 1.3 Descriptive statistics
-## • Summary for the main variables in the transformed dataset
+## Summary od the main variables in the transformed dataset
 ## *Numeric variables*
@@
 
-## 1.4.2 Country
-
-### • The lowest price is 12 EUR per night (Czech Republic),  whereas the lowest average cost is 86 EUR (Poland). On average, Austrian accommodation is the most expensive with a mean price of 158 EUR.
-
-```{r echo=FALSE}
-datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-# Graph to show the correlation pattern by each country:
-```{r echo=FALSE}
-ggplot(corr_table1, aes(x = correlation ,
-                       y = fct_reorder(country, correlation))) +
-  geom_point(color = 'red', size = 2)+
-  labs(y='Countries',x='Correlation')
-```
-
-## 1.4.3 Distance
+## 1.4.2 Distance
 
@@
 
+## 1.4.3 Country
+
+### • The lowest price is 12 EUR per night (Czech Republic),  whereas the lowest average cost is 86 EUR (Poland). On average, Austrian accommodation is the most expensive with a mean price of 158 EUR.
+
+```{r echo=FALSE}
+datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+# Graph to show the correlation pattern by each country:
+```{r echo=FALSE}
+ggplot(corr_table1, aes(x = correlation ,
+                       y = fct_reorder(country, correlation))) +
+  geom_point(color = 'red', size = 2)+
+  labs(y='Countries',x='Correlation')
+```
+
 ## 1.5 Hypothesis testing

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 ```
+# Graph to show the correlation pattern by each country:
+```{r echo=FALSE}
+ggplot(corr_table1, aes(x = correlation ,
+                       y = fct_reorder(country, correlation))) +
+  geom_point(color = 'red', size = 2)+
+  labs(y='Countries',x='Correlation')
+```
 
@@
   kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-# Graph to show the correlation pattern by each country:
-```{r echo=FALSE}
-ggplot(corr_table1, aes(x = correlation ,
-                       y = fct_reorder(country, correlation))) +
-  geom_point(color = 'red', size = 2)+
-  labs(y='Countries',x='Correlation')
 ```

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 ## 1.3 Descriptive statistics
-## Summary od the main variables in the transformed dataset
+# Summary of the main variables in the transformed dataset
 ## *Numeric variables*

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

@@
 ## 1.3 Descriptive statistics
-# Summary of the main variables in the transformed dataset
+#Summary of the main variables in the transformed dataset
 ## *Numeric variables*
